### 2012-11-10 doc/progress_plan/report.tex
Created opening paragraphs with citations

\section{Project Summary}

@@

\renewcommand{\refname}{Initial Bibliography} 
\bibliographystyle{plain}
\nocite{*}
\bibliography{report}

>>>>

\section{Project Summary}
Partridge is a web-based tool designed to assist research and knowledge
acquisition in the domain of scientific papers.

With the advent of the 'Digital Age' and the ability of computers to copy and
reproduce information for a negligible cost, the amount of information
available to researchers is increasing drastically.  Bj\"{o}rk's 2009 study
suggests that approximately 1.4 Million papers were published in the year 2006
alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
publishing (making papers available for free online\cite{Suber2012}) across
most scientific disciplines is providing researchers with an even larger volume
of information to be processed. It logically follows that as the amount of
general information grows, the proportion of relevant material becomes harder
to find without the assistance of complicated information filtering and retrieval
systems.

Partridge aims to autonomously process as many scientific papers as
possible to facilitate intelligent filtering and recommendations to
researchers, who would otherwise be required to manually browse thousands of
online documents. This should reduce the amount of information that the user is
required to process themselves, thereby speeding up the research process.

@@

\renewcommand{\refname}{Initial Bibliography} 
\bibliographystyle{plain}
\bibliography{report}
